Predicting Internet Path Dynamics and Performance with Machine Learning

### 2017-12-20 paper-tex/paper.tex
merge

\maketitle
\hui{I think we should focus on the process not the final result, which is also important.}
\section{Introduction}

@@

2. we find some drawbacks in their data. For instance, the route change times problem discussed in github. And the way they process the data.

3. we try some other models to get better performance like xgboost and LSTM.

\section{Related Works}
1. we introduce the original paper in details

>>>>

  \maketitle

\hui{I think we should focus on the process not the final result, which is also important.}

\section{Introduction}

@@

Internet paths change frequently due to inter/intra-domain routing changes, load balancing, and even misconfigurations and failures. Some of these changes can seriously disrupt performance, causing longer round-trip times, congestion, or even loss of connectivity. Thus, it is of great significant to predict Internet path dynamics and performance.

The dataset it provides with is a full week of Paris \texttt{traceroute} measurements performed through the M-Lab open

Internet measurement initiative. The author observes more than 450,000 different paths sampled through Paris-traceroute measurements from more than 180 geo-distributed servers. However, most of the paths are not periodically sampled during this week. And only 2,346 paths have at least 100 \texttt{traceroute} measurements during the analyzed week. So the dataset only contains corresponding infomation of these 2,346 paths.

We find some drawbacks in their data process.

The author processes the data and calculates some statistics for the whole seven days and then use the data to get the ramdon forest model.

\section{Related Works}

1. introduce the original paper

In the original paper, the problem they solve is to use random forest model to predict three labels for one path: $(i)$ the remaining life time of a path (i.e., the time before a path changes), $(ii)$ the number of path changes in a future timeslot, and $(iii)$ the average RTT of a path in the next \texttt{traceroute} measurement.

And to achieve these three targets, 69 input features are used to describe the  statistical properties of route dynamics and path latency.

For the first route dynamic target, the first group of 11 features,referred to as $F_A$, is chosen. It describes the statistical properties (average, minimum, maximum, and percentiles) of the route duration observed for each path.

And for the second target, the second group of 14 features, as $F_B$, are relevant to the prediction of number of route changes. $F_B$ features take into account the statistical properties of route changes. In addition to that, $F_B$ contains information about the number of route changes observed for a path so far and a binary feature indicating whether a route change occurred for a path in the current time slot.

And the last group of 44 features ,referred to as $F_C$ decribes statistical properties of path latency, which is relavent to the prediction of the next \texttt{traceroute} measurement. They calculate the staistical properties of four RTT metrics (average, minimum, maximum and standard deviation) reported from each \texttt{traceroute} measurement.
